---
title: "p8105_hw5_JL6047"
author: "Eric Luo"
date: "2022-11-17"
output: github_document
---
Load Packages
```{r}
library(tidyverse)
library(viridis)
library(dplyr)
library(purrr)
```


Problem#2

Read file, and create a new variable "city_state" according to instruction
```{r}
raw = read_csv(file = "./homicide-data.csv")
raw$city_state = paste(raw$city,raw$state,sep=", ")
```
Rearrange the data,filter out the mistaken parameter where Tulsa is located in OK not AL

```{r}

homicide_city = raw%>%
  select(city_state,everything())%>%
  filter(city_state != "Tulsa, AL")

```

Count numbers of homicides and unsolved cases for each city

```{r}

Summary = homicide_city%>%
group_by(city_state) %>%
  summarise(homicides = n(),
            unsolved_homicides = sum(disposition != "Closed by arrest")) 
```

Run prop.test on Baltimore and pull out CIs'
```{r}
Bal_test = prop.test(
  x = Summary %>% filter(city_state == "Baltimore, MD") %>% pull(unsolved_homicides), 
  n = Summary %>% filter(city_state == "Baltimore, MD") %>% pull(homicides)
) 

Bal_test

Bal_test %>% broom::tidy()

est_prop = Bal_test %>% broom::tidy() %>%
  pull(estimate) %>%
  round(digit = 3)
conf_low = Bal_test %>% broom::tidy() %>%
  pull(conf.low) %>%
  round(digit = 3)
conf_high = Bal_test %>% broom::tidy() %>%
  pull(conf.high) %>%
  round(digit = 3)
```


Extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.
```{r}


All_test = 
  Summary %>% 
  mutate(prop_test = map2(.x = unsolved_homicides, .y = homicides, ~prop.test(x = .x, n = .y)),
         tidy_test = map(.x = prop_test, ~broom::tidy(.x))) %>% 
  select(city_state, tidy_test) %>% 
  unnest(tidy_test) %>% 
  select(city_state, estimate, conf.low, conf.high)
All_test

```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
All_test %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(x = "City",
       y = "Estimate",
       title = "Estimates and Confidence Intervals of Porportion of Unsolved Homicides for Each City") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  theme(plot.title = element_text(size = 15))
```



Problem#3

Define a function that runs t test for the input data
```{r}
sim_t_test = function(n = 30, mu, sigma = 5){
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma)
  ) 
  
  test_data = t.test(sim_data, mu = 0, conf.level = 0.95)
  
  sim_data %>% 
    summarize(
      mu_hat = pull(broom::tidy(test_data), estimate),
      p_val = pull(broom::tidy(test_data), p.value)
    )
}
```
run the function for 5000 times
```{r}
set.seed(1) 
sim_results_df = 
  tibble(mean = c(0:6)) %>% 
  mutate(
    output_lists = map(.x = mean, ~rerun(5000, sim_t_test(mu = .x))),
    estimate_dfs = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)
```

Draw a plot showing proportion of rejected nulls on y-axis and true mu on x-axis
According to the plot, the proportion of rejection of null increases with increasing effect size. There is a positive association between effect size and powers of test. And there association is stronger at smaller effect size.
```{r}
sim_results_df %>%
  group_by(true_mean) %>%
  summarise(
    count = n(),
    rej_num = sum(p_val < 0.05),
    rej_prop = rej_num/count
  ) %>%
  ggplot(aes(x = true_mean, y = rej_prop)) +
  geom_point() +
  geom_line() + 
  geom_text(aes(label = round(rej_prop, 3)), vjust = -1, size = 4) + 
  scale_x_continuous(n.breaks = 10) +
  scale_y_continuous(n.breaks = 6) +
  labs(
    title = "Size vs. Power",
    x = "True Mean",
    y = "Power"
  )
```


Now we make the plot showing the average estimate of mu on  y-axis and the true value of mu on the x-axis.
```{r}
sim_results_df %>%
  group_by(true_mean) %>%
  summarise(
    avg_mu_hat = mean(mu_hat)
  ) %>%
  ggplot(aes(x = true_mean, y = avg_mu_hat)) +
  geom_point() +
  geom_line() + 
  geom_text(aes(label = round(avg_mu_hat, 3)), vjust = -1, size = 3) + 
  scale_x_continuous(n.breaks = 6) +
  scale_y_continuous(n.breaks = 6) +
  labs(
    title = "True Mean vs Average Estimate of Mean",
    x = "True Mean",
    y = "Average Estimate of Mean"
  )
```


Overlay with a second plot to check on rejected samples with y-axis of estimate of mu and x-axis of true value
```{r}
overall_df = sim_results_df %>%
  group_by(true_mean) %>%
  summarise(
    avg_mu_hat = mean(mu_hat)
  ) 
sim_results_df %>%
  filter(p_val < 0.05) %>%
  group_by(true_mean) %>%
  summarise(
    avg_mu_hat = mean(mu_hat)
  ) %>%
  ggplot(aes(x = true_mean, y = avg_mu_hat, color = "Rejected samples")) +
  geom_point() +
  geom_line() + 
  geom_text(aes(label = round(avg_mu_hat, 3)), vjust = -1, size = 3) +
  geom_point(data = overall_df, aes(x = true_mean, y = avg_mu_hat, color = "All samples")) +
  geom_line(data = overall_df, aes(x = true_mean, y = avg_mu_hat, color = "All samples")) +  
  geom_text(data = overall_df, aes(label = round(avg_mu_hat, 3), color = "All samples"), vjust = 2, size = 3) +
  scale_x_continuous(n.breaks = 6) +
  scale_y_continuous(n.breaks = 6) +
  labs(
    title = "Association Between True Mean and Average Estimate of Mean",
    x = "True Mean",
    y = "Average Estimate of Mean",
    color = "Type"
  ) +
  scale_color_manual(values = c("All samples" = "black", "Rejected samples" = "red"))
```

From plot above, we can see that the sample average of mu across tests for all samples is approximately equal to the true value of mu.
On the other side, however, the sample average of mu across rejection is only nearly equal when mu=4,5,6 but not for mu=1,2,3.
So we reject the null hypothesis at larger mu's because of a larger effect size.

